Cartogram Mapping and its Application to Cancer Data Visualization

### 2019-09-27 review_article.Rmd
vancouver referencing style, will need to fix up text in some spots

---
title: "Cartogram Mapping and its Application to Cancer Data Visualization"
author: "Stephanie Kobakian, Jessie Roberts and Dianne Cook"
bibliography: reviewbib.bib
output:
  pdf_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_depth: 3
  word_document:
    toc: yes
    toc_depth: '3'
link-citations: yes
fontsize: 11pt
biblio-style: vancouver
yolo: yes
---

>>>>

---
title: "Cartogram Mapping and its Application to Cancer Data Visualization"
author: "Stephanie Kobakian, Jessie Roberts and Dianne Cook"
bibliography: reviewbib.bib
output:
  pdf_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_depth: 3
  word_document:
    toc: yes
    toc_depth: '3'
link-citations: yes
fontsize: 11pt
csl: vancouver.csl
yolo: yes
---
